The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-03-31 methods/ms.tex
Testing ...
deconv_map changed to deal with NANs better

For the purposes of comparison with other surveys, we present in
Appendix \ref{app:ReferenceSources} a selection

@@

Figure \ref{fig:deconv_filter} shows the fraction of flux recovered in the maps
as a function of the deconvolution kernel used to create the astrophysical model
maps.  The differences at large source sizes are not yet well-understood
(!!!!!!), but at the smallest source size, it is evident that a deconvolution
kernel smaller than the source size does not fully recover the source flux.
Therefore we chose a deconvolution kernel smaller than the beam but larger than
the pixel size used. \ref{fig:Deconvolution} demonstrates the effects of using
both too large and too small a kernel.

>>>>

For the purposes of comparison of both flux and pointing with other
surveys, we present in Appendix \ref{app:ReferenceSources} a selection
of bright, compact, relatively isolated sources.

@@

Figure \ref{fig:deconv_filter} shows the fraction of flux recovered in the maps
as a function of the deconvolution kernel used to create the astrophysical model
maps.  The differences at large source sizes are not yet well-understood
(!!!!!!), but at the smallest source size, it is evident that a deconvolution
kernel smaller than the source size does not fully recover the source flux.
Therefore we chose a deconvolution kernel smaller than the beam but larger than
the pixel size used.  Figure \ref{fig:Deconvolution} demonstrates the effects of using
both too large and too small a kernel.
